Modularizing Street Map Generation \\ \vspace{8pt} \large An Adventure in Tensors

### 2013-12-12 paper/paper.tex
pipeline intro

\section{Pipeline}

>>>>

\section{Pipeline}
We begin with a set of user constraints, which illustrate the general shape of
the roads on the blank canvas. These can be linear or radial, and can be input
as JSON. From these we generate a tensor field, and from that, major and minor
eigenvector fields, which describe the direction stipulate by the constraints at
every point in the area. Finally, based on these eigenvector fields, we generate
seed points from which to trace streamlines across the map. These streamlines
produce the final roads.

\todo{insert pipeline diagram}
